---
title: "EDS241: Assignment 2"
author: "Charles Hendrickson"
date: '`r format(Sys.time(), "%m/%d/%Y")`'
output: 
  pdf_document:
    toc: false
    number_sections: yes
header-includes:
  - \setlength{\parindent}{1em}
  - \usepackage{float}
--- 
  
``` {r setup, echo = FALSE, message = FALSE, warning = FALSE}

# set default chunk options
knitr::opts_chunk$set(fig.width = 4, fig.height = 3, 
                      echo = TRUE, message = FALSE, warning = FALSE)


# load packages
packages=c("stargazer", "here", "tidyr", "dplyr","stringr", "janitor", 
           "cowplot", "ggplot2", "tinytex", "datasets", "tibble", "openxlsx", "estimatr", "car", "readxl")

# Load estimatr package
library(estimatr)

for (i in packages) {
  if (require(i,character.only=TRUE)==FALSE) {
    install.packages(i,repos='http://cran.us.r-project.org')
  }
  else {
    require(i,character.only=TRUE)
  }
}

#devtools::install_github('rstudio/rmarkdown')
options(scipen=10) # not scientific notation

```

Load the NBP.xls data 
```{r}
# load data 
nbp_data <- read_excel("data/NBP.xls")

```

\noindent (a) Make a histogram depicting the distribution of Dnox_masstons.

```{r}
ggplot(data = nbp_data, aes(x = Dnox_masstons)) +
  geom_histogram() +
  labs(title = "Distribution of the change in annual nitrogen oxides (NOx) emissions
from all power plants in U.S. counties between 2000 and 2008", 
x = "Change in annual nitrogen oxides 
(NOx) emissions (in tons)",
y = "Number of U.S. Counties")
  
```

\noindent (b) Create an indicator =1 if the county has PctBlack above the sample median, and =0 otherwise (in the rest of the assignment, I refer to this variable as ‘D’). What is the average of PctBlack for counties above the median, i.e. counties for which D=1?

**The average of PctBlack for counties above the median (counties for which D=1) is  19.31375%.**

```{r}
# Create new column called "D" which is an indicator that equals 1 if the county has PctBlack above the sample median, and equals 0 otherwise

# First, find the sample median for PctBlack
PctBlack_median <- median(nbp_data$PctBlack)

# Second, create a new variable called "D" by using "ifelse", which takes a condition, followed by what the output should be if the condition is met, followed by the output of the condition is not met.
nbp_data <- nbp_data %>%
  mutate(D = ifelse(PctBlack > PctBlack_median, 1, 0))

# Third, find the average of PctBlack for counties above the median (counties for which D=1)

avg_PctBlack_D1 <- nbp_data %>%
  filter(D == 1)%>% 
  summarise(mean_PctBlack = mean(PctBlack)) %>% 
  as.numeric()

print(avg_PctBlack_D1)
```

\noindent (c) Estimate a regression of Dnox_masstons on NBP. Interpret the estimated intercept and the coefficient on NBP.

**The estimated intercept means that for U.S. counties that were not regulated under the NOx Budget Program, the change in annual NOx emissions between 2000 and 2008 from all power plants in that county was -3.622 tons on average.**

**The estimated coefficient on NBP means that the difference in the change in annual NOx emissions (2000 to 2008) between power plants in a county regulated under the NOx Budget Program (NBP) and power plants in a county unregulated under the NBP is -3.920 tons on average.**


```{r}
# Regress Dnox_masstons on NBP
lm_robust(Dnox_masstons ~ NBP, data = nbp_data)

```

\noindent (d) Create an interaction between the variables NBP and D. Estimate a regression of Dnox_masstons on NBP, D, and this interaction. Interpret each estimated regression coefficient, including the intercept.

**The estimated intercept means that for U.S. counties that were not regulated under the NOx Budget Program, the change in annual NOx emissions between 2000 and 2008 from all power plants in that county was -3.714107 tons on average.**

**The estimated coefficient on NBP means that the difference in the change in annual NOx emissions (2000 to 2008) between power plants in a county regulated under the NOx Budget Program (NBP) and power plants in a county unregulated under the NBP is -3.933890 tons on average.**

**The estimated regression coefficient for "D" means that the difference in the change in annual NOx emissions (2000 to 2008) between power plants in a county with an African American population above the sample median and a county with an African American population below the sample median is 0.197928 tons on average.**

```{r}
# Creates a linear model 
lm_robust(Dnox_masstons ~ NBP + D + , data = nbp_data)
```


(e) What is the predicted Dnox_masstons in a county that was not regulated under NBP and where PctBlack is above the sample median (i.e., where D=1)? Report the 95% confidence interval for this prediction. Make sure to use “heteroskedasticity-robust” standard errors.

**The predicted Dnox_masstons in a county that was not regulated under NBP and where PctBlack is above the sample median is -3.516179 tons.**



```{r}
Dnox_masstons = -3.714107 + (-3.933890)*(0) + (0.197928)*(1)

print(Dnox_masstons)
```































































